01-deseq2

### 2019-03-14 scripts/00-datawrangling.Rmd
read write files

```{r write}
write.csv(colData_manipluation, "../results/colData_manipluation.csv", row.names = TRUE) 
write.csv(countData_manipluation, "../results/countData_manipluation.csv", row.names = TRUE) 
write.csv(colData_characterization, "../results/colData_characterization.csv", row.names = TRUE) 
write.csv(countData_characterization, "../results/countData_characterization.csv", row.names = TRUE) 
```

>>>>

```{r write}
write.csv(colData_manipluation, "../results/00-colData-manipluation.csv", row.names = TRUE) 
write.csv(countData_manipluation, "../results/countData-manipluation.csv", row.names = TRUE) 
write.csv(colData_characterization, "../results/00-colData-characterization.csv", row.names = TRUE) 
write.csv(countData_characterization, "../results/00-countData-characterization.csv", row.names = TRUE) 
```

### 2019-03-14 scripts/01-DESeq2.Rmd
read write files

```{r deseq2}
dds <- DESeqDataSetFromMatrix(countGonad, colGonad, ~ sex*treatment)
dds # view the DESeq object - note numnber of genes
dds <- dds[ rowSums(counts(dds)) > 1, ]  # Pre-filtering genes with 0 counts
dds # view number of genes afternormalization and the number of samples
dds <- DESeq(dds) # Differential expression analysis
vsd <- vst(dds, blind=FALSE) ## variance stabilized
head(assay(vsd),3)
#write.csv(assay(vsd), file = "../results/01-vsd.csv", row.names = T)
```

>>>>

Now, I'll do RNAseq on all the data from the parental care characterization study.

```{r}
colData <- read.csv("../results/00-colData_characterization.csv", header = T, row.names = 1)
countData <- read.csv("../results/00-countData_characterization.csv", header = T, row.names = 1)
```

```{r deseq2}
dds <- DESeqDataSetFromMatrix(countData, colData, ~ sex*treatment)
dds # view the DESeq object - note numnber of genes
dds <- dds[ rowSums(counts(dds)) > 1, ]  # Pre-filtering genes with 0 counts
dds # view number of genes afternormalization and the number of samples
dds <- DESeq(dds) # Differential expression analysis
vsd <- vst(dds, blind=FALSE) ## variance stabilized
#head(assay(vsd),3)
#write.csv(assay(vsd), file = "../results/01-vsd.csv", row.names = T)
```
